Frustratingly easy multi-domain, multilingual translation with latent multi-task group dropout

### 2021-11-04 2022/acl/acl_latex.tex
add mdmt scores

%new commands
\def\-{\raisebox{.75pt}{-}}
\usepackage{mathtools,xparse}
\DeclarePairedDelimiter{\abs}{\lvert}{\rvert}
\DeclarePairedDelimiter{\norm}{\lVert}{\rVert}
\NewDocumentCommand{\normL}{ s O{} m }{%
  \IfBooleanTF{#1}{\norm*{#3}}{\norm[#2]{#3}}_{2}%
}
\newcommand{\domain}[1]{\texttt{\textsc{#1}}}
%\newcommand{\system}[1]{\texttt{{#1}}}
%\renewcommand{\UrlFont}{\ttfamily\small}
%\renewcommand{\S}{\scriptsize}
%\newcommand{\R}{\mathbb{R}}
%\newcommand{\vect}[1]{\boldsymbol{#1}}
%\DeclareMathOperator*{\argmax}{argmax}
%\DeclareMathOperator*{\argmin}{argmin}
%\usepackage[draft]{todo}
%\newcommand{\fyTodo}[1]{\Todo[FY:]{\textcolor{orange}{#1}}}
%\newcommand{\fyTodostar}[1]{\Todo*[FY:]{\textcolor{orange}{#1}}}
%\newcommand{\fyDone}[1]{\done[FY]\Todo[FY:]{\textcolor{orange}{#1}}}
%\newcommand{\fyDonestar}[1]{\done[FY]\Todo[FY:]{\textcolor{orange}{#1}}}
%\newcommand{\fyFuture}[1]{\done[FY]\Todo[FY:]{\textcolor{red}{#1}}}

@@

\section{Multi-task group dropout}
We define a group dropout for a domain $d$ as follow
\begin{equation}
\begin{array}{rcl}
\tilde{h}^l &=& h^l \odot r_l^d ,\\
r_l^d \in \{ 0,1 \}^{d_k}, \\
h^{l+1} &=& \text{LAYER}^{l+1}(h^l) ,\\
l & \in & [0,\cdots,L] ,\\
\end{array}
\end{equation}
where $L$ is number of Transformer layers of our NMT model, the binary vector $r_l^d$ is a dropping mask. The dropping mask $r_l^d$ of $l^{th}$ layer and domain $d$ is defined as follow
\begin{equation}
\begin{array}{rcl}
r_l^d(i) &=& \begin{cases\newcommand{\domain}[1]{\texttt{\textsc{#1}}}
\newcommand{\system}[1]{\texttt{{#1}}}}
      1, & \text{if}\ p \times \frac{d_k}{n_p} \leqslant i < (p+1) \times \frac{d_k}{n_p} \\
      & \text{AND} \  m_l^d(p) \text{\small ==} 1 \\
      0, & \text{otherwise},
    \end{cases} \\
p & \in & \{0,\dots,n_p\text{-}1 \}, \\
d & \in & \{0,\dots,n_d\text{-}1 \}, \\
i & \in & \{0,\dots,d_k\text{-}1 \}, \\
m_l^d & \in & \{0,1\}^{n_p} \ \forall d,l \, \\
\mid m_l^d \mid_{L_1} & = & k , \\
\Delta^{n_p}_k & = & \{ m \in \{0,1\}^{n_p} | \mid m \mid_{L_1} = k \},
\end{array}
\end{equation}
where $n_p$ is the number of dropout groups; $n_d$ is the number of domains; $d_k$ is the size of Transformer layers; $k$ is the number of retained groups at each layer; $m_l^d$ is a binary vector indicating which group of the nodes of the $l^{th}$ layer is dropped in the sub-network modeling domain $d$. The group $p$ is retained for domain $d$ if $m_l^d(p)\text{small ==}1$ and is dropped if $m_l^d(p)\text{small ==}0$. We also denote $\Delta^{n_p}_k$ the set of all admissible dropping masks.

We incorporate the latent variables $m_{l\in[0,\cdots,L]}^d$ into the log-likelihood of our model as below. For the sake of brevity, we denote $m_l^d$ the set of latent variables $m_{l\in[0,\cdots,L]}^d$
\begin{equation}
\hspace{-1.5em}
\begin{array}{rcl}
\text{log} P(y|x,\theta,d) & \text{=} & \text{log} P(y, m_l^d |x,\theta,d) \text{-} \text{log} P(m_l^d|y, x,\theta,d) \\
& \text{=} & \mathbb{E}_{P(m_l^d | \Phi_l^d)} \big[ \text{log} P(y, m_l^d | x,\theta,d) \text{-} \text{log} P(m_l^d | \Phi_l^d) \big] \\
& \text{+} & KL(P(m_l^d | \Phi_l^d) \parallel P(m_l^d|y, x,\theta,d)) \\
& \geq & \mathbb{E}_{P(m_l^d | \Phi_l^d)} \big[ \text{log} P(y, m_l^d | x,\theta,d) \text{-} \text{log} P(m_l^d | \Phi_l^d) \big]  \\
& \text{=} & \mathbb{E}_{P(m_l^d | \Phi_l^d)} \big[ \text{log} P(y | x,\theta,m_l^d, d) \big] \\
& \text{-} & KL \big( P(m_l^d | \Phi_l^d) \parallel P(m_l^d | x,\theta,d) \big) \\
& \text{=} & \mathcal{L}(\theta, \Phi_l^d, x , y) \label{eq:lower-bound}
\end{array}
\end{equation}
our training objective will be the lowerbound, which is called the evidence lower bound (ELBO) in variational statistic \citep{Diederick14auto}, $\mathcal{L}(\theta, \Phi_l^d, x , y)$. The variational distribution of $m_l^d$, $P(m_l^d|\Phi_l^d)$, is defined as follows
\begin{equation}
\hspace{-2.em}
\begin{array}{rcl}
\Phi_d & \in & \mathbb{R}^{n_p} , \\
Ind^d & \text{=} & \{ i_1, \cdots, i_k \} \ | \ \Phi_l^d \\
& \sim & \ \text{\small Sampling\_without\_replacement} \big(\text{softmax}(\Phi_l^d) \big) , \\
m_l^d(i) &\text{=}& \mathbb{I}(i \in Ind^d) .\\
\end{array}
\end{equation}

@@

\begin{equation}
\begin{array}{rcl}
T_1 &=& \mathbb{E}_{P(m_l^d | \Phi_l^d)} \big[ \text{log} P(y | x,\theta,m_l^d, d)  \big] \\
&=& \mathbb{E}_{g_l^d(p) \sim Gumbel(0,1) \ \text{i.i.d}} \big[ \text{log} P(y | x,\theta,\tilde{m}_l^d,d) \big] \\
\end{array}
\end{equation}
where
\begin{equation}
\begin{array}{rcl}
g_l^d & \in & \mathbb{R}^{n_p} \\
g_l^d(p) & \sim & Gumbel(0,1) \ \text{i.i.d} \\
&& \forall p \in \{ 0,\cdots,n_p\text{-}1 \} \\
i_1, \cdots, i_k &=& Top\_k \ \{ \ g_l^d(0) + \Phi_l^d(0), \cdots,\\ &&g_l^d(n_p\text{-}1) + \Phi_l^d(n_p\text{-}1) \ \} \\
\tilde{m}_l^d(p) &=& \mathbb{I}(p \in Ind^d). \\
\end{array} \label{eq:top-k}
\end{equation}

\begin{align}
T_2 &= - KL \big( P(m_l^d | \Phi_l^d) \parallel P(m_l^d | x,\theta,d) \big) \\ 
	&= \mathbb{H} \big[ P(m_l^d | \Phi_l^d) \big] - \text{log}(\#\Delta^{n_p}_k) \\ 
	&= \mathbb{H} \big[ P(i_1,\cdots,i_k | \Phi_l^d) \big] - \text{log}(\#\Delta^{n_p}_k) \\ \
	&\geqslant \mathbb{H} \big[ P(i_1 | \Phi_l^d) \big] - \text{log}(\#\Delta^{n_p}_k) \label{eq:entropy}
\end{align}

@@

\begin{equation}
\begin{array}{rcl}
 \hat{m}_l^d(\tau) &=&\displaystyle{\mathop{argmin}_{\substack{
       0 \leqslant m_i \leqslant 1 \ \forall 0 \leqslant i \leqslant n_d\text{-}1 \\
        1^{T}.m = k
      }}} -(g_l^d+\Phi_l^d)^{T} . m - \tau H_b(m) \\
& \text{in which} & \\
H_b(m) &=& - \sum_i m_i \text{log}(m_i) + (1-m_i)\text{log}(1-m_i)
\end{array}
\label{eq:soft-top-k}
\end{equation}

In Appendix \ref{appendix:a}, we will prove that $\lim_{\tau \rightarrow 0}\hat{m}_l^d(\tau) = \tilde{m}_l^d$. Furthermore, we will also provide the computation of $\hat{m}_l^d(\tau)$ and prove that $\hat{m}_l^d(\tau)$ is a differentiable function w.r.t $\Phi_l^d$ and its differentiation is computed via implicit differentiation theorem. During the training, we approximate $\tilde{m}_l^d$ by $\hat{m}_l^d(\tau)$ by gradually decaying the hyperparameter $\tau$ to $0$. The gradient of the term $T_1$ w.r.t $\Phi_l^d$ is computed via the chain rule as follows
\begin{equation}
\frac{\partial T_1}{\Phi_l^d} = \frac{\partial T_1}{\hat{m}_l^d(\tau)} \times \frac{\hat{m}_l^d(\tau)}{\Phi_l^d}
\end{equation}
The gradient $\frac{\partial T_1}{\hat{m}_l^d(\tau)}$ is computed via autograd algorithm while $\frac{\hat{m}_l^d(\tau)}{\Phi_l^d}$ is computed via implicit differentiation, that we will explain carefully in Appendix \ref{appendix:a}.
\section{Experimental settings}
\subsection{Baselines}
\subsubsection{Multi-domain, multilingual translation}
In both cases, we examinate the performance of three following MT systems.
\begin{itemize}
	\item Transformer trained with .
	\item Adapter based Transformer.
	\item Transformer with multi-task group dropout.
\end{itemize}
For the sake of brevity, we put the detailed descriptions of these systems in Appendix \ref{appendix:c}.
\subsection{Datasets}
\subsubsection{Multi-domain translation}
We reuse the same data of a recent work of \citet{Pham21revisiting} in multi-domain translation. For the sake of brevity, we leave most of the details of data in Appendix \ref{appendix:c}.
\subsubsection{Multilingual translation}
We evaluate our model on both one-to-many (O2M) and many-to-one (M2O)
translation tasks. We evaluate models on widely used multilingual translation datasets.
\begin{itemize}
	\item TED8-Related. Following the setting of \citep{Wang20balancing}, we use a subset of translations between English and eight related languages.
	\item TED8-Diverse. The dataset consists of parallel sentences between English and eight diverse languages \citep{Wang20balancing}.
\end{itemize}
The detailed description of the datasets is provided in Appendix \ref{appendix:c}.
\section{Results and ablation studies}
\subsection{Multi-domain translation}
\subsection{Multilingual translation}
\subsection{Similarity between dropping masks}
\section{Related work}
\section{Conclusions and outlook}
\bibliography{bibliography}
\bibliographystyle{acl_natbib}
\appendix
\section{Appendix A}
\label{appendix:a}
Proof of limit. Computation of $\hat{m}_l^d(\tau)$. Theorem of implicit differentiation and Proof of differentiability.
\section{Appendix B}
\label{appendix:b}
In this section, we give a simple proof of Inequality \ref{eq:entropy}. In fact, we only need to prove $\mathbb{H} \big[ P(i_1,\cdots,i_k | \Phi_l^d) \big] \geqslant \mathbb{H} \big[ P(i_1 | \Phi_l^d) \big]$. The proof is as follows
\begin{align*}
&\mathbb{H} \big[ P(i_1,\cdots,i_k | \Phi_l^d) \big] = - \mathbb{E}_{i_1,\cdots,i_k | \Phi_l^d} \big[ \text{log}P(i_1,\cdots,i_k | \Phi_l^d) \big] \\
&= -\mathbb{E}_{i_1,\cdots,i_k | \Phi_l^d} \big[ \displaystyle{\sum_{j=2}^k}\text{log}P(i_j | i_1,\cdots,j_{j-1},\Phi_l^d) +  \text{log} P(i_1 | \Phi_l^d) \big] \\
&\geqslant -\mathbb{E}_{i_1,\cdots,i_k | \Phi_l^d} \big[ \text{log} P(i_1 | \Phi_l^d) \big] \\
&= -\mathbb{E}_{i_1 | \Phi_l^d} \big[ \text{log} P(i_1 | \Phi_l^d) \big] = \mathbb{H} \big[ P(i_1 | \Phi_l^d) \big]
\end{align*}
\section{Appendix C}
\label{appendix:c}
\subsection{Multi-domain translation}

>>>>

\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{longtable}
\usepackage{tikz}
\usetikzlibrary{calc}
\usepackage[draft]{todo}
\usepackage[normalem]{ulem}
\usepackage{xspace}
\usepackage{amsmath,amsfonts,amssymb}

\newcommand{\fyTodo}[1]{\Todo[FY:]{\textcolor{orange}{#1}}}
\newcommand{\fyTodostar}[1]{\Todo*[FY:]{\textcolor{orange}{#1}}}
\newcommand{\fyDone}[1]{\done[FY]\Todo[FY:]{\textcolor{orange}{#1}}}
\newcommand{\fyFuture}[1]{\done[FY]\Todo[FY:]{\textcolor{red}{#1}}}
\newcommand{\fyDonestar}[1]{\done[FY]\Todo[FY:]{\textcolor{orange}{#1}}}
\newcommand{\jcTodo}[1]{\Todo[JC:]{\textcolor{red}{#1}}}
\newcommand{\jcDone}[1]{\done[JC]\Todo[JC:]{\textcolor{red}{#1}}}
\newcommand{\revision}[1]{\textcolor{black}{#1}}
\newcommand{\revisiondone}[1]{\textcolor{black}{#1}}
\newcommand{\revisiondel}[1]{}
\newcommand{\src}{\ensuremath{\mathbf{f}}} % source sentence
\newcommand{\trg}{\ensuremath{\mathbf{e}}} % target sentence
\newcommand{\domain}[1]{\texttt{\textsc{#1}}}
\newcommand{\system}[1]{\texttt{{#1}}}

@@

\section{Multi-task group dropout}
We define a group dropout for a domain $d$ as follow
\begin{equation}
\begin{array}{rcl}
\tilde{h}^l &=& h^l \odot r_l^d ,\\
r_l^d \in \{ 0,1 \}^{d_k}, \\
h^{l+1} &=& \text{LAYER}^{l+1}(h^l) ,\\
l & \in & [0,\cdots,L] ,\\
\end{array}
\end{equation}
where $L$ is number of Transformer layers of our NMT model, the binary vector $r_l^d$ is a dropping mask. The dropping mask $r_l^d$ of $l^{th}$ layer and domain $d$ is defined as follow
\begin{equation}
\begin{array}{rcl}
r_l^d(i) &=& \begin{cases}
      1, & \text{if}\ p \times \frac{d_k}{n_p} \leqslant i < (p+1) \times \frac{d_k}{n_p} \\
      & \text{AND} \  m_l^d(p) \text{\small ==} 1 \\
      0, & \text{otherwise},
    \end{cases} \\
p & \in & \{0,\dots,n_p\text{-}1 \}, \\
d & \in & \{0,\dots,n_d\text{-}1 \}, \\
i & \in & \{0,\dots,d_k\text{-}1 \}, \\
m_l^d & \in & \{0,1\}^{n_p} \ \forall d,l \, \\
\mid m_l^d \mid_{L_1} & = & k , \\
\Delta^{n_p}_k & = & \{ m \in \{0,1\}^{n_p} | \mid m \mid_{L_1} = k \},
\end{array}
\end{equation}
where $n_p$ is the number of dropout groups; $n_d$ is the number of domains; $d_k$ is the size of Transformer layers; $k$ is the number of retained groups at each layer; $m_l^d$ is a binary vector indicating which group of the nodes of the $l^{th}$ layer is dropped in the sub-network modeling domain $d$. The group $p$ is retained for domain $d$ if $m_l^d(p)\text{small ==}1$ and is dropped if $m_l^d(p)\text{small ==}0$. We also denote $\Delta^{n_p}_k$ the set of all admissible dropping masks.

We incorporate the latent variables $m_{l\in[0,\cdots,L]}^d$ into the log-likelihood of our model as below. For the sake of brevity, we denote $m_l^d$ the set of latent variables $m_{l\in[0,\cdots,L]}^d$
\begin{equation}
\hspace{-1.5em}
\begin{array}{rcl}
\text{log} P(y|x,\theta,d) & \text{=} & \text{log} P(y, m_l^d |x,\theta,d) \text{-} \text{log} P(m_l^d|y, x,\theta,d) \\
& \text{=} & \mathbb{E}_{P(m_l^d | \Phi_l^d)} \big[ \text{log} P(y, m_l^d | x,\theta,d) \text{-} \text{log} P(m_l^d | \Phi_l^d) \big] \\
& \text{+} & KL(P(m_l^d | \Phi_l^d) \parallel P(m_l^d|y, x,\theta,d)) \\
& \geq & \mathbb{E}_{P(m_l^d | \Phi_l^d)} \big[ \text{log} P(y, m_l^d | x,\theta,d) \text{-} \text{log} P(m_l^d | \Phi_l^d) \big]  \\
& \text{=} & \mathbb{E}_{P(m_l^d | \Phi_l^d)} \big[ \text{log} P(y | x,\theta,m_l^d, d) \big] \\
& \text{-} & KL \big( P(m_l^d | \Phi_l^d) \parallel P(m_l^d | x,\theta,d) \big) \\
& \text{=} & \mathcal{L}(\theta, \Phi_l^d, x , y) \label{eq:lower-bound}
\end{array}
\end{equation}
our training objective will be the lowerbound, which is called the evidence lower bound (ELBO) in variational statistic \citep{Diederick14auto}, $\mathcal{L}(\theta, \Phi_l^d, x , y)$. The variational distribution of $m_l^d$, $P(m_l^d|\Phi_l^d)$, is defined as follows

\begin{align}
\hspace{-2.em}
&\Phi_d \in \mathbb{R}^{n_p} , \nonumber \\
&Ind^d \text{=}  \{ i_1, \cdots, i_k \} \nonumber \\
&\sim \text{\small Sampling\_without\_replacement} \big(\text{softmax}(\Phi_l^d) \big) , \nonumber \\
&m_l^d(i) \text{=} \mathbb{I}(i \in Ind^d) .\nonumber
\end{align}

@@

\begin{align}
\hspace{-2.em}
T_1 &= \mathbb{E}_{P(m_l^d | \Phi_l^d)} \big[ \text{log} P(y | x,\theta,m_l^d, d)  \big] \nonumber \\
&= \mathbb{E}_{g_l^d(p) \displaystyle{\mathop{\sim}^{\text{i.i.d}}} Gumbel(0,1) \ } \big[ \text{log} P(y | x,\theta,\tilde{m}_l^d,d) \big] \nonumber
\end{align}
where
\begin{align}
\hspace{-2.em}
g_l^d & \in \mathbb{R}^{n_p} \nonumber \\
g_l^d(p) & \displaystyle{\mathop{\sim}^{\text{i.i.d}}} Gumbel(0,1) \nonumber \\
& \forall p \in \{ 0,\cdots,n_p\text{-}1 \} \nonumber \\
i_1, \cdots, i_k &= Top\_k \ \{ \ g_l^d(0) + \Phi_l^d(0), \cdots, \label{eq:top-k} \\ 
&g_l^d(n_p\text{-}1) + \Phi_l^d(n_p\text{-}1) \ \} \nonumber \\
\tilde{m}_l^d(p) &= \mathbb{I}(p \in Ind^d). \nonumber 
\end{align}
%
\begin{align}
T_2 &= - KL \big( P(m_l^d | \Phi_l^d) \parallel P(m_l^d | x,\theta,d) \big) \nonumber \\ 
	&= \mathbb{H} \big[ P(m_l^d | \Phi_l^d) \big] - \text{log}(\#\Delta^{n_p}_k) \nonumber \\ 
	&= \mathbb{H} \big[ P(i_1,\cdots,i_k | \Phi_l^d) \big] - \text{log}(\#\Delta^{n_p}_k) \nonumber \\ \
	&\geqslant \mathbb{H} \big[ P(i_1 | \Phi_l^d) \big] - \text{log}(\#\Delta^{n_p}_k) \label{eq:entropy}
\end{align}

@@

\begin{align}
\hat{m}_l^d(\tau) &= \displaystyle{\mathop{argmin}_{\substack{
       0 \leqslant m_i \leqslant 1 \ \forall 0 \leqslant i \leqslant n_d\text{-}1 \label{eq:soft-top-k}\\
        1^{T}.m = k
      }}} -(g_l^d+\Phi_l^d)^{T} . m - \tau H_b(m) \\
& \text{in which} \nonumber \\
H_b(m) &= - \sum_i m_i \text{log}(m_i) + (1-m_i)\text{log}(1-m_i) \nonumber 
\end{align}

In Appendix \ref{appendix:a}, we will prove that $\lim_{\tau \rightarrow 0}\hat{m}_l^d(\tau) = \tilde{m}_l^d$. Furthermore, we will also provide the computation of $\hat{m}_l^d(\tau)$ and prove that $\hat{m}_l^d(\tau)$ is a differentiable function w.r.t $\Phi_l^d$ and its differentiation is computed via implicit differentiation theorem. During the training, we approximate $\tilde{m}_l^d$ by $\hat{m}_l^d(\tau)$ by gradually decaying the hyperparameter $\tau$ to $0$. The gradient of the term $T_1$ w.r.t $\Phi_l^d$ is computed via the chain rule as follows
\begin{equation}
\frac{\partial T_1}{\Phi_l^d} = \frac{\partial T_1}{\hat{m}_l^d(\tau)} \times \frac{\hat{m}_l^d(\tau)}{\Phi_l^d}
\end{equation}
The gradient $\frac{\partial T_1}{\hat{m}_l^d(\tau)}$ is computed via autograd algorithm while $\frac{\hat{m}_l^d(\tau)}{\Phi_l^d}$ is computed via implicit differentiation, that we will explain carefully in Appendix \ref{appendix:a}.
\section{Experimental settings}
\subsection{Baselines}
\subsubsection{Multi-domain, multilingual translation}
In both cases, we examinate the performance of three following MT systems.
\begin{itemize}
	\item Transformer trained with .
	\item Adapter based Transformer.
	\item Transformer with multi-task group dropout.
\end{itemize}
For the sake of brevity, we put the detailed descriptions of these systems in Appendix \ref{appendix:c}.
\subsection{Datasets}
\subsubsection{Multi-domain translation}
We reuse the same data of a recent work of \citet{Pham21revisiting} in multi-domain translation. For the sake of brevity, we leave most of the details of data in Appendix \ref{appendix:c}.
\subsubsection{Multilingual translation}
We evaluate our model on both one-to-many (O2M) and many-to-one (M2O)
translation tasks. We evaluate models on widely used multilingual translation datasets.
\begin{itemize}
	\item TED8-Related. Following the setting of \citet{Wang20balancing}, we use a subset of translations of \citet{qi18when} between English and eight related languages.
	\item TED8-Diverse. The dataset consists of parallel sentences between English and eight diverse languages as in \citet{Wang20balancing}.
\end{itemize}
The detailed description of the datasets is provided in Appendix \ref{appendix:c}.
\section{Results and ablation studies}
\subsection{Multi-domain translation}
According to Table \ref{tab:mdmt}, \system{LaMGD} shows a significant improvement over the generic system \system{Transformer} with zero extra parameters. Moreover, \system{LaMGD} achieve equivalent performance in average compared to \system{Adapter}, which is carrefully finetuned with a approximately 12.4M additional parameters.
\begin{table*}
  \centering
  \begin{tabular}{|p{4cm}|*{7}{r|}} \hline
    Model / Domain & \multicolumn{1}{c|}{\domain{ med}} & \multicolumn{1}{c|}{\domain{ law}} & \multicolumn{1}{c|}{\domain{bank}} & \multicolumn{1}{c|}{\domain{talk}} & \multicolumn{1}{c|}{\domain{ it }} & \multicolumn{1}{c|}{\domain{ rel}} & \multicolumn{1}{c|}{\domain{avg}} \\ \hline 
    \system{Transformer}  \hfill{\footnotesize[65m]} & 40.3 & 59.5 & 49.8 & 36.4 & 49.0 & 80.0  & 52.5\\
    \revision{\system{Adapter}}   \hfill{\footnotesize[+12.4m]}  & 39.5 & 61.0 & 53.1 & 37.5 & 49.6 & 91.0 & 55.28 \\ 
    \system{LaMGD}   \hfill{\footnotesize[+0m]}  & 40.3 & 60.4 & 52.4 & 39.0 & 52.4 & 87.5 & 55.33 \\ 
    \hline
  \end{tabular}
  \caption{Multi-domain translation}
  \label{tab:mdmt}
\end{table*}
\subsection{Multilingual translation}

\subsection{Similarity between dropping masks}
\section{Related work}
\section{Conclusions and outlook}
\bibliography{bibliography}
\bibliographystyle{acl_natbib}
\appendix
\section{Appendix A}
\label{appendix:a}
Proof of limit. Computation of $\hat{m}_l^d(\tau)$. Theorem of implicit differentiation and Proof of differentiability.
\section{Appendix B}
\label{appendix:b}
In this section, we give a simple proof of Inequality \ref{eq:entropy}. In fact, we only need to prove $\mathbb{H} \big[ P(i_1,\cdots,i_k | \Phi_l^d) \big] \geqslant \mathbb{H} \big[ P(i_1 | \Phi_l^d) \big]$. The proof is as follows
\begin{align*}
&\mathbb{H} \big[ P(i_1,\cdots,i_k | \Phi_l^d) \big] = - \mathbb{E}_{i_1,\cdots,i_k | \Phi_l^d} \big[ \text{log}P(i_1,\cdots,i_k | \Phi_l^d) \big] \\
&= -\mathbb{E}_{i_1,\cdots,i_k | \Phi_l^d} \big[ \displaystyle{\sum_{j=2}^k}\text{log}P(i_j | i_1,\cdots,j_{j-1},\Phi_l^d) +  \text{log} P(i_1 | \Phi_l^d) \big] \\
&\geqslant -\mathbb{E}_{i_1,\cdots,i_k | \Phi_l^d} \big[ \text{log} P(i_1 | \Phi_l^d) \big] \\
&= -\mathbb{E}_{i_1 | \Phi_l^d} \big[ \text{log} P(i_1 | \Phi_l^d) \big] = \mathbb{H} \big[ P(i_1 | \Phi_l^d) \big]
\end{align*}
\section{Appendix C}
\label{appendix:c}
\subsection{Multi-domain translation}
